Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-04 paper.tex
conclusion?!

To estimate the uncertainty on fuel cycle output metrics, a ``Total Monte
Carlo'' approach has been applied. In the following, output metric uncertainty
corresponds to the Standard Deviation of the output metrics over about 200
different simulations. For each uncertainty associated parameter, an
artificially large uncertainty of $10\%$ have been Normally distributed.

@@

Two main points can be deduced from this work. First of all, in a transitional
fuel cycle, the uncertainty contributions to an output metric can vary over time
depending of various factors: deployment schedule artifact or pressure point in
the material flows.

>>>>

To estimate the uncertainty on fuel cycle output metrics, a ``Total Monte
Carlo'' approach has been applied. In the following, output metric uncertainty
corresponds to the Standard Deviation of the output metrics over about 200
different simulations. For each deployed facilities, the uncertainty associated
parameters have been a normally distributed with an artificially large standard
deviation of $10\%$.

@@

\section{Conclusion}

Two main points can be deduced from this work. Firstly, in a transitional
fuel cycle, the uncertainty contributions to an output metric can vary over time
depending of various factors: deployment schedule artifact or pressure point in
the material flows.

Secondly, it is important to note the special character of the time related
parameters uncertainty in a fuel cycle study, such as cooling time and cycle
length. As the cycle length impact the discharge fuel burnup, it also affects
the frequency of the fuel loads, this, as well as the cooling may imply a
uncertainty on the material availability, which could lead to a large
uncertainty. Those kind of uncertainties will need a special treatment on further
uncertainty analysis.

This study aims to be a proof-of-principle for uncertainty propagation in
potential commercial fuel cycle transition and will to be extended to random
uncertainty.

While the parameters contributing to natural uranium needs and fissile inventory
uncertainties might be obvious, such study allows to estimate each parameters
contribution, it could be less obvious for other parameters, such as
plutonium quality, waste compositions. Such studies could also provide research
guidance for nuclear archeology works, which aims to precisely estimate past
fissile production by the different nuclear countries.
